Data_Processing

### 2021-04-20 Code/Data_Processing.Rmd
Data Processing updates

# Load Packages
library(tidyverse)
library(lubridate)
library(plyr)
library(stringr)
library(tidyr)
library(zoo)

@@

#### Trying to fill in the missing values with previous value - doesn't work with a list/string
#IV_tracklogs_ascending1 <- 
#  IV_tracklogs_ascending %>% 
#  fill(use, use, .direction = 'down')

@@

@@

>>>>

# Load Packages
library(tidyverse)
library(lubridate)
library(plyr)
library(stringr)
library(tidyr)

@@

#### Attempted code: Trying to fill in the missing values with previous value - doesn't work with a list/string
#IV_tracklogs_ascending1 <- 
#  IV_tracklogs_ascending %>% 
#  fill(use, use, .direction = 'down')

@@

### Attempted code to fill use_num with blanks where use doesnt have a character and fill with previous number when it does. 
# ifelse(IV_tracklogs_ascending$use != "[0-9]+", IV_tracklogs_ascending$use_num == "", fill(use_num, use_num, .direction = 'down'))

@@

## Summarizing Data Structure

```{r}
# Ranges of dates
range(IV_tracklogs$date)
range(IV_wpts$date)

# Range and central tendancies of trail widths
range(IV_tracklogs_ascending$use_num)
mean(IV_tracklogs_ascending$use_num)
median(IV_tracklogs_ascending$use_num)

# Range of lattitude and longitude
range(IV_tracklogs$lat)
mean(IV_tracklogs$lat)
median(IV_tracklogs$lat)

range(IV_tracklogs$lon)
mean(IV_tracklogs$lon)
median(IV_tracklogs$lon)

# unique values for use_cha
unique(IV_tracklogs_ascending$use_cha)
